\chapter*{Abstract}
The rapid growth of IoT devices in recent years has shaped everyday life more profoundly than most technological advancements in history. 
As with any widespread innovation, this global adoption brings both benefits and drawbacks. 
The conveniences introduced by IoT and smart devices are now integral to modern life, making them difficult for society to forgo. 
However, the rising number of these devices also opens up more potential attack surfaces for malicious actors. 
When considering that many of these devices accompany individuals nearly constantly, the threat to personal privacy rises substantially.

This project focuses on one specific aspect of the problem: its objective is to prevent the unauthorized recording of sensitive conversations through microphones.
The selected methodology to achieve the objective is to execute a Denial of Service (DoS) attack on the microphones by overwhelming them with ultrasonic sound waves.
To demonstrate the effectiveness of this method, a fully functional prototype device capable of executing the attack has been developed.

This report provides a detailed explanation of each step in the development process, starting with the analysis of microphone technologies and a review of state-of-the-art attacks targeting them, followed by the formulation of the core concept, and concluding with its final implementation.
To facilitate a deeper understanding of its functionality, the report includes a comprehensive explanation of each component and of the source code.

The prototype device has been thoroughly tested on the most common types of devices, including smartphones, PCs, and smartwatches, across various distance ranges, and has demonstrated highly promising results.
The reports concludes with an analysis of the known issues and of the areas that could be furtherly improved in the future in order to deliver a product even more effective, reliable and feature-rich.